---
title: "Credit Card Marketing"
output: html_notebook
---


```{r}
library(pacman)
p_load(rpart, tidyverse, rpart.plot)
CreditCard <- read.csv("Credit Card.csv")
CreditCard <- CreditCard %>% na.omit()
#View(CreditCard)
```

Classification Tree

```{r}

Tree <- rpart(Accepted ~ Reward + MailerType + IncomeLevel + NumBankAccountsOpen + OverdraftProtection + CreditRating + NumCreditCardsHeld + NumHomesOwned + HouseholdSize + OwnYourHome + AverageBalance, data=CreditCard, control = rpart.control(cp = 0.0001))

bestcp <- Tree$cptable[which.min(Tree$cptable[,"xerror"]),"CP"]

prunedTree <- prune(Tree, cp = bestcp)

rpart.plot(prunedTree, type = 5)
```


```{r}
prp(prunedTree,
type = 4, 
clip.right.labs = FALSE, 
extra = 101,
under = TRUE, 
under.cex = 1, 
fallen.leaves = TRUE, 
box.palette = "RdYlGn", 
branch = .3, 
round = 0, 
leaf.round = 9,
prefix = "Accepted", 
main = "Credit Card Marketing",
cex.main = 1.5, 
branch.col = "gray",
branch.lwd = 2) 
```


ROC Curve- Classification Tree(Non-Partitioned)

```{r}
p_load(ROCR)

PredictedAcceptedProbabilities <- predict(prunedTree)

ROC_Predictions <- prediction(predictions = PredictedAcceptedProbabilities, labels = CreditCard$Accepted)

ROC_Performance <- performance(ROC_Predictions, "sens", "fpr")

plot(ROC_Performance, xlab = "False Positive Rate (1 - Specificity)", ylab="Sensitivity")
AUC <- performance(ROC_Predictions, "auc")
AUC <- as.numeric(AUC@y.values[1])
text(0.8,0.2, paste("AUC = " , round(AUC,3)))
abline(0,1)
```

Confusion Matrix

```{r}
p_load(caret)
cutoff <- 0.5
PredictedClass <- as.factor(ifelse(PredictedAcceptedProbabilities >= cutoff, 1, 0))
Targets <- as.factor(CreditCard$Accepted)
ConfusionMatrix <- caret::confusionMatrix(data=PredictedClass, reference = Targets, positive="1")
ConfusionMatrix
```


Classification Tree (Partitioned)

```{r}
set.seed(112321)
library(pacman, tidyverse, ROCR)
p_load(rpart, tidyverse, rpart.plot)

#Add in the row number - unique ID
CreditCard <- CreditCard %>% mutate(
                              id = row_number())

# Sample randomly 70% to be our training set:
CreditCardTrain <- CreditCard %>% sample_frac(0.7)

#Take the rest (anti-join) to be our test set:
CreditCardTest <- CreditCard %>% anti_join(CreditCardTrain, by="id")

```


```{r}
Tree <- rpart(Accepted ~ Reward + MailerType + IncomeLevel + NumBankAccountsOpen + OverdraftProtection + CreditRating + NumCreditCardsHeld + NumHomesOwned +  OwnYourHome , data=CreditCardTrain, control = rpart.control(cp = 0.0001))

bestcp <- Tree$cptable[which.min(Tree$cptable[,"xerror"]),"CP"]

prunedTree <- prune(Tree, cp = bestcp)

rpart.plot(prunedTree, type = 5)

```



```{r}
prp(prunedTree,
type = 4, 
clip.right.labs = FALSE, 
extra = 101,
under = TRUE, 
under.cex = 1, 
fallen.leaves = TRUE, 
box.palette = "RdYlGn", 
branch = .3, 
round = 0, 
leaf.round = 9,
prefix = "Accepted", 
main = "Credit Card Marketing",
cex.main = 1.5, 
branch.col = "gray",
branch.lwd = 2) 
```




ROC Curve (Partitioned)
```{r}
#In the training set:
PredictedAcceptedProbabilitiesTrain <- predict(prunedTree)
ROC_Predictions_Train <- prediction(predictions = PredictedAcceptedProbabilitiesTrain, labels = CreditCardTrain$Accepted)
ROC_Performance_Train <- performance(ROC_Predictions_Train, "sens", "fpr")
plot(ROC_Performance_Train, xlab = "False Positive Rate (1 - Specificity)", ylab="Sensitivity", lty=1, col="red")
AUC_Train <- performance(ROC_Predictions_Train, "auc")
AUC_Train <- as.numeric(AUC_Train@y.values[1])
text(0.8,0.2, paste("AUC Train= " , round(AUC_Train,3)))

##Now in the Test Set: 
PredictedAcceptedProbabilitiesTest <- predict(prunedTree, newdata=CreditCardTest)
ROC_Predictions_Test <- prediction(predictions = PredictedAcceptedProbabilitiesTest, labels = CreditCardTest$Accepted)
ROC_Performance_Test <- performance(ROC_Predictions_Test, "sens", "fpr")
plot(ROC_Performance_Test, xlab = "False Positive Rate (1 - Specificity)", ylab="Sensitivity", add=TRUE, lty=2, col="green")
AUC_Test <- performance(ROC_Predictions_Test, "auc")
AUC_Test <- as.numeric(AUC_Test@y.values[1])
text(0.8,0.1, paste("AUC Test= " , round(AUC_Test,3)))
```


Random Forest


```{r}

set.seed(112321)
p_load(rpart, tidyverse, rpart.plot, randomForest, ROCR)


#Add in the row number - unique ID
CreditCard <- CreditCard %>% mutate(
                              id = row_number())

# Sample randomly 70% to be our training set:
CreditCardTrain <- CreditCard %>% sample_frac(0.7)

#Take the rest (anti-join) to be our test set:
CreditCardTest <- CreditCard %>% anti_join(CreditCardTrain, by="id")
```

ntree = how many trees in the forest? 
mtry = how many predictor variables in each tree? 
importance = calculate variable importance? 
sampsize = how many observations in each tree? 

```{r}
forest <- randomForest(as.factor(OfferAccepted) ~ Reward + MailerType + IncomeLevel + NumBankAccountsOpen + OverdraftProtection + CreditRating + NumCreditCardsHeld + NumHomesOwned + HouseholdSize + OwnYourHome + AverageBalance, data=CreditCardTrain, ntree=2000, mtry = 2, importance = TRUE, sampsize = nrow(CreditCardTrain), replace = TRUE)
```

Variable Importance

```{r}
View(forest$importance)
```

ROC Curve-Random Forest

```{r}
pred <- as.numeric(predict(forest, type="prob", newdata=CreditCardTest)[,2])
New_ROC_Predictions <- prediction(predictions = pred, labels = CreditCardTest$OfferAccepted)
New_ROC_Performance <- performance(New_ROC_Predictions, "sens", "fpr")
plot(New_ROC_Performance, xlab = "False Positive Rate (1 - Specificity)", ylab="Sensitivity")
NewAUC <- performance(New_ROC_Predictions, "auc")
NewAUC <- as.numeric(NewAUC@y.values[1])
text(0.8,0.2, paste("AUC = " , round(NewAUC,3)))
abline(0,1)
```
